---
title: "Alcohol vs Seat choice"
author: "Michelle Coleman"
date: "February 15, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows that the heavy drinkers are mostly in the back.

## Numerical Summarys 

```{r}
 favstats(alcohol~Seat,data=davisdata)
```

People that sit in the back drinks extremely more alcohol than the people in the middle and the front per this data.

## Inferential Tests

# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is so small that it is unlikely that the consumption of alcohol in all three selections of seats are the same.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

The TukeyHSD plot shows that people in the back drink more than the ones in the middle and the front drink less than everyone. There's no evidence of alcohol consumption being the same


## Conclusions


